---
title: "557 Project Analysis"
output: github_document
---
```{r}
library(tibble)
library(BSDA)
```

## Outcome #1: Number (Percentage) of Participants Reporting a ≥ 50% Reduction in Headache Days Code (Fisher Test)


```{r setup}

# For Topiramate vs Placebo
outcome1.top <- matrix(c(58, 72, 26,40), nrow = 2, byrow = TRUE)

rownames(outcome1.top) <- c("Topiramate", "Placebo")
colnames(outcome1.top) <- c("No Reduction in Headaches", "Reduction in Headaches")

outcome1.top <- as.data.frame(outcome1.top)

fisher_result_top <- fisher.test(outcome1.top)
print(fisher_result_top)


# For Amitriptyline vs Placebo 
outcome1.ami <- matrix(c(63, 69, 26, 40), nrow = 2, byrow = TRUE)

rownames(outcome1.ami) <- c("Amitriptyline", "Placebo")
colnames(outcome1.ami) <- c("No Reduction in Headaches", " Reduction in Headaches")

outcome1.ami <- as.data.frame(outcome1.ami)

fisher_result_ami <- fisher.test(outcome1.ami)
print(fisher_result_ami)

# For Topiramate vs Amitriptyline

outcome1.together <- matrix(c(58, 72, 63, 69), nrow = 2, byrow = TRUE)

rownames(outcome1.together) <- c("Topiramate", "Amitriptyline")
colnames(outcome1.together) <- c("No Reduction in Headaches", " Reduction in Headaches")

outcome1.together <- as.data.frame(outcome1.together)

fisher_result_together <- fisher.test(outcome1.together)
print(fisher_result_together)



```


## Outcome #2: Changes in Absolute Headache Disability Score on PEDIMAS Code (two sample ttest)

```{r}

# Data for Topiramate
mean_Topiramate<- -26.8
sd_Topiramate <- 27.5
n_Topiramate <- 130

# Data for Placebo
mean_Placebo <- -22.6
sd_Placebo <- 29.42
n_Placebo <- 66

# Data for Amitriptyline
mean_Amitriptyline<- -22.5
sd_Amitriptyline <- 26.37
n_Amitriptyline <- 132

#For Topiramate vs Placebo
tsum.test(
  mean_Topiramate,
  s.x = sd_Topiramate,
  n.x = n_Topiramate,
  mean.y = mean_Placebo,
  s.y = sd_Placebo,
  n.y = n_Placebo,
  alternative = "two.sided",
  mu = 0,
  var.equal = FALSE,
  conf.level = 0.95
)

# For Amitriptyline vs Placebo 
tsum.test(
  mean_Amitriptyline,
  s.x = sd_Amitriptyline,
  n.x = n_Amitriptyline,
  mean.y = mean_Placebo,
  s.y = sd_Placebo,
  n.y = n_Placebo,
  alternative = "two.sided",
  mu = 0,
  var.equal = FALSE,
  conf.level = 0.95
)
# For Topiramate vs Amitriptyline 
tsum.test(
  mean_Topiramate,
  s.x = sd_Topiramate,
  n.x = n_Topiramate,
  mean.y = mean_Amitriptyline,
  s.y = sd_Amitriptyline,
  n.y = n_Amitriptyline,
  alternative = "two.sided",
  mu = 0,
  var.equal = FALSE,
  conf.level = 0.95
)


```


##  Outcome #3: Change in number of headache days Code (two sample ttest)

```{r}

# Data for Topiramate
mean_Topiramate<- -6.7
sd_Topiramate <- 4.99
n_Topiramate <- 101

# Data for Placebo
mean_Placebo <- -5.9
sd_Placebo <- 6.96
n_Placebo <- 59

# Data for Amitriptyline
mean_Amitriptyline<- -6.7
sd_Amitriptyline <- 6.20
n_Amitriptyline <- 104

#For Topiramate vs Placebo
tsum.test(
  mean_Topiramate,
  s.x = sd_Topiramate,
  n.x = n_Topiramate,
  mean.y = mean_Placebo,
  s.y = sd_Placebo,
  n.y = n_Placebo,
  alternative = "two.sided",
  mu = 0,
  var.equal = FALSE,
  conf.level = 0.95
)



# For Amitriptyline vs Placebo 
tsum.test(
  mean_Amitriptyline,
  s.x = sd_Amitriptyline,
  n.x = n_Amitriptyline,
  mean.y = mean_Placebo,
  s.y = sd_Placebo,
  n.y = n_Placebo,
  alternative = "two.sided",
  mu = 0,
  var.equal = FALSE,
  conf.level = 0.95
)

# For Topiramate vs Amitriptyline 
tsum.test(
  mean_Topiramate,
  s.x = sd_Topiramate,
  n.x = n_Topiramate,
  mean.y = mean_Amitriptyline,
  s.y = sd_Amitriptyline,
  n.y = n_Amitriptyline,
  alternative = "two.sided",
  mu = 0,
  var.equal = FALSE,
  conf.level = 0.95
)

```


## Outcome #4: Tolerability as Indicated by the Percentage of Participants that Completed the 24 weeks Treatment Phase Code (Fisher Test)

```{r}
# For Topiramate vs Placebo 
outcome4.top <- matrix(c(28, 102, 7, 59), nrow = 2, byrow = TRUE)

rownames(outcome4.top) <- c("Topiramate", "Placebo")
colnames(outcome4.top) <- c("Not Tolerable", " Tolerable")

outcome4.top <- as.data.frame(outcome4.top)

fisher_result_top <- fisher.test(outcome4.top)
print(fisher_result_top)


# For Amitriptyline vs Placebo 
outcome4.ami <- matrix(c(26, 106, 7, 59), nrow = 2, byrow = TRUE)

rownames(outcome4.ami) <- c("Amitriptyline", "Placebo")
colnames(outcome4.ami) <- c("Not Tolerable", " Tolerable")

outcome4.ami <- as.data.frame(outcome4.ami)

fisher_result_ami <- fisher.test(outcome4.ami)
print(fisher_result_ami)

# For Topiramate vs Amitriptyline 

outcome4.together <- matrix(c(28, 102, 26, 106), nrow = 2, byrow = TRUE)

rownames(outcome4.together) <- c("Topiramate", "Amitriptyline")
colnames(outcome4.together) <- c(" Not tolerable", "Tolerable")

outcome4.together <- as.data.frame(outcome4.together)

fisher_result_together <- fisher.test(outcome4.together)
print(fisher_result_together)
```

## Outcome 5: Occurence of Treatment Emergent Serious Adverse Effects Code (Fisher Test)
```{r}
# For Topiramate vs Placebo 
outcome5.top <- matrix(c(141, 4, 70, 2 ), nrow = 2, byrow = TRUE)

rownames(outcome5.top) <- c("Topiramate", "Placebo")
colnames(outcome5.top) <- c("No Serious Adverse Effect", "Serious Adverse Effect")

outcome5.top <- as.data.frame(outcome5.top)

fisher_result_top <- fisher.test(outcome5.top)
print(fisher_result_top)


# For Amitriptyline vs Placebo 

outcome5.ami <- matrix(c(138, 6, 70, 2), nrow = 2, byrow = TRUE)

rownames(outcome5.ami) <- c("Amitriptyline", "Placebo")
colnames(outcome5.ami) <- c("No Serious Adverse Effect", " Serious Adverse Effect")

outcome5.ami <- as.data.frame(outcome5.ami)

fisher_result_ami <- fisher.test(outcome5.ami)
print(fisher_result_ami)

# For Topiramate vs Amitriptyline 

outcome5.together <- matrix(c(141, 4, 138, 6), nrow = 2, byrow = TRUE)

rownames(outcome5.together) <- c("Topiramate", "Amitriptyline")
colnames(outcome5.together) <- c("No Serious Adverse Effect", " Serious Adverse Effect")

outcome5.together <- as.data.frame(outcome5.together)

fisher_result_together <- fisher.test(outcome5.together)
print(fisher_result_together)
```

